Casual Bandits

### 2016-01-10 causal-bandit/icml-2015/causal-bandits-icml.tex
minor fixes

Note that algorithms designed for finite-armed bandits would explore interventions more uniformly and achieve a regret of $\Omega\left(\sqrt{N/T}\right)$.
This is a significant improvement, since $m \leq N$ is usually substantially smaller than $N$.

>>>>

Note that algorithms designed for finite-armed bandits would explore interventions more uniformly and achieve a regret of $\Omega(\sqrt{N/T})$.
Since $m$ is typically much smaller than $N$ we anticipate that the new algorithm will significantly outperform classical bandit algorithms in
this setting.
